---
title: "Quarto template"
format: 
  pdf:
    toc: true
    highlight-style: atom-one
editor: source
---


# Quarto vs Rmarkdown

Note `Quarto` (`.qmd` file) is just a "new", more flexible `Rmarkdown` (`.rmd` file).

The only difference I've noticed for our purposes, when including R code, is: 

* instead of including code chunk options between the code chunk opening's curly braces "`{...}`", 
* the options are specified in the lines below starting the line with "`#|`"

So in Rmarkdown you might do the following (ignore the first comment character "`#`" on each line in the below code chunk):

```{r, eval=FALSE}
# <!-- Rmarkdown version -->
#```{r, some_option = "option value", some_other_option = FALSE}
# ... some code ...
#```
```

You equivalently do (ignore the first comment character "`#`" on each line in the below code chunk):



```{r, eval=FALSE}
# <!-- Quarto version -->
# ```{r}
# #| some_option: "option value"
# #| some_other_option: false
# ... some code ...
#```
```

## A more comprehensive list of differences

[This FAQ page](https://quarto.org/docs/faq/rmarkdown.html)


## An example

If reading this from the pdf output - please see the `.qmd` code chunk to see what generates this code/ouput.

```{r}
#| include: true
#| echo: true
x <- 10
x
```




